Association between SARS-CoV-2 and metagenomic content of samples from the Huanan Seafood Market

### 2023-07-03 paper/paper.tex
revisions for Virus Evolution (#4)
* acknowledge Ben Pierce

* add reviewer comments

* Reviewer 1 comment 1: better caveat date of emergence estimates

* Reviewer 1 point 2: discuss epi of market more

* Reviewer point 3: de-emphasize 20% cutoff

* Reviewer 1 point 4: samples inconclusive on origins

* Reviewer 2 point 1

* Reviewer 2 point 2: methods rationale

* Reviewer 2 point 3: mapping quality ensures uniquely mapped only

* update competing interests

* Reviewer 2 point 4: consistency of calling samples + vs -

* Reviewer 2 comment 3: move figure to supplement

* code for Reviewer 2 co

To create an mitochondrial genome alignment reference set, I followed a procedure partially analogous to that described by \citet{crits2023genetic}.
Note that a similar analysis could also be implemented using more standard metagenomic analysis tools such as Kraken2~\citep{wood2019improved}, as was in fact done in the Chinese CDC study~\citep{liu2023surveillance}.
The reasons for instead implementing the pipeline used here were as follows:
\begin{itemize}
\item To ensure comparability to \citet{crits2023genetic} by using an approach that parallels the one they described.
\item To use a reference set that includes all of the potentially susceptible species sold at the market: many of these species lack full nuclear genomes on RefSeq, and one (Amur hedgehog) doesn't even have a mitochondrial genome on RefSeq. Therefore, the manual process used to build the mitochondrial reference set described below was necessary to ensure all these species were in the reference.
\end{itemize}

>>>>

To create an mitochondrial genome alignment reference set, I followed a procedure partially analogous to that described by \citet{crits2023genetic}.
Note that a similar analysis could also be implemented using more standard metagenomic analysis tools such as Kraken2~\citep{wood2019improved}, as was in fact done in the Chinese CDC study~\citep{liu2023surveillance}.
The reasons for instead implementing the pipeline used here were two-fold.
First, to ensure comparability to \citet{crits2023genetic} by using an approach that parallels the one they described.
Second, to use a reference set that includes all of the potentially susceptible species sold at the market: many of these species lack full nuclear genomes on RefSeq, and one (Amur hedgehog) doesn't even have a mitochondrial genome on RefSeq.
Therefore, the manual process used to build the mitochondrial reference set described below was necessary to ensure all these species were in the reference.
